The magnetosphere structure of a Kerr black hole: marginally force-free equatorial boundary condition

### 2018-08-19 paper/ms.tex
done

Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
{\bf On this point $r_{\rm LS}|_{\mu=0}$,  the LS function $\mathcal K$ vanishes,
and $I$ must also vanish for satisfying the boundary condition (\ref{eq:bc3}),
which in turns indicates a vanishing angular velocity $\Omega$ from
the radiation condition (\ref{eq:rad}), i.e. $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$. 
Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ into $\mathcal K = 0$,
we obtain $r_{\rm LS}|_{\mu=0}=2$. i.e.
to satisfy the boundary condition (\ref{eq:bc3}), the LS must intersect the equator at $r=2$, which also
justifies our choice of equatorial boundary conditions (\ref{eq:bc2},\ref{eq:bc3}) . }
% From the expression of the LS function (\ref{eq:ls}), it is straightforward to see
% $ r_+ \leq r_{\rm LS}|_{\mu=0} \leq 2$ for $0 \leq \Omega \leq \Omega_{\rm H}$.
%  Due to the frame-dragging effect, $\Omega$
% must be non-zero inside the ergosphere.
%Therefore the only possibility is  $r_{\rm LS}|_{\mu=0} = 2$,

@@

Motivated by these simulation results, we revisit the problem of the uniform field solution in this paper.
We find the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
condition (\ref{eq:bc3}) are rather informative, which dictate the BH magnetosphere structure
in various aspects, including the shape of the LS, the near-horizon field line configuration and
the source of BZ flux (see Section \ref{subsec:features} for details). Other than these qualitative properties,
we also propose an algorithm for numerically solving the GS equation and consistently imposing
the marginally force-free equatorial boundary condition. As a result, we find a good agreement
between our numerical solutions with the high-accuracy FFE simulations.

>>>>

Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
{\bf On this point $r_{\rm LS}|_{\mu=0}$ where the LS function $\mathcal K$ vanishes,
$I$ must also vanish for satisfying the marginally boundary condition (see Equation [\ref{eq:B2mE2}]),
which in turns indicates a vanishing angular velocity $\Omega$ from
the radiation condition (\ref{eq:rad}), i.e., $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$.
Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ back into $\mathcal K = 0$,
we obtain $r_{\rm LS}|_{\mu=0}=2$. i.e.
to satisfy the boundary condition (\ref{eq:bc3}), the LS must intersect the equator at $r=2$, which also
justifies our choice of equatorial boundary conditions (\ref{eq:bc2},\ref{eq:bc3}) . }

@@

Motivated by these simulation results, we revisit the problem of the uniform field solution in this paper.
We find the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
condition (\ref{eq:bc3}) are rather informative, which dictate the BH magnetosphere structure
in various aspects, including the shape of the LS, the near-horizon field line configuration and
the source of BZ flux (see Section \ref{subsec:features} for details). {\bf Especially we find the LS
intersects with the ergosphere at the equator, which was also observed in previous simulations \cite[e.g.][]{Carrasco2017, East2018}
and now we understand its underlying physics.}
Other than these qualitative properties,
we also propose an algorithm for numerically solving the GS equation and consistently imposing
the marginally force-free equatorial boundary condition. As a result, we find a good agreement
between our numerical solutions with the high-accuracy FFE simulations.

### 2018-08-19 paper/reply.tex
done

Pan et al.  proposed that the two eigenfunctions are not independent;
instead, they are related by the radiation condition at infinity, which is formulated as
$\hat E_\theta = \hat B_\phi$, with $\hat E_\theta$ and $\hat B_\phi$ being the $\theta$
component of electric field and $\phi$ component of the magnetic field measured
by zero-angular-momentum-observers, respectively.
As for the uniform field solution, the radiation condition is explicitly expressed as
\[ I = 2\Omega A_\phi, \]
which has been readily confirmed by recent high-accuracy FFE simulations (East2018).

@@

{\bf 3) The argument for the LS intersecting the ergosphere boundary on the equator needs
clarification. I found it hard to follow, and I was easily able to find a counter-example to the first
statement (a=.1, Omega=.15; there are two zeros of K on the equator, both at r>2). }

{\bf Finally, a suggestion:
• The proof that the inner light cylinder intersects the ergosphere boundary at the equator is
a very nice result (assuming it is correct). A few groups have seen that the current sheet
ends at the ergosphere in full simulations but people seem sheepish about making the claim
because of numerical resolution. The analytical argument is a big help here, so the author
might consider emphasizing the point more somehow.}

We thank the referee for comments that we feel have .

>>>>

To give more information about the radiation condition, I revise the relevant statement as follows:

``Pan et al.  proposed that the two eigenfunctions are not independent;
instead, they are related by the radiation condition at infinity, which is formulated as
$\hat E_\theta = \hat B_\phi$, with $\hat E_\theta$ and $\hat B_\phi$ being the $\theta$
component of electric field and $\phi$ component of the magnetic field measured
by zero-angular-momentum-observers, respectively.
As for the uniform field solution, the radiation condition is explicitly expressed as
\[ I = 2\Omega A_\phi, \]
which has been readily confirmed by recent high-accuracy FFE simulations. " \\

@@

To clarify the definition of LS, I have added a sentence following the LS function formula:

``The GS equation degrades to first order on the LS, where $\mathcal K(r,\theta; \Omega )$
vanishes. " \\

{\bf 3) The argument for the LS intersecting the ergosphere boundary on the equator needs
clarification. I found it hard to follow, and I was easily able to find a counter-example to the first
statement (a=.1, Omega=.15; there are two zeros of K on the equator, both at $r>2$). }

The referee's comment makes me realize the problem of the original argument, which I have reorginized as follows:

``Let's first find out where the LS intersects with the equator, $r_{\rm LS}|_{\mu=0}$.
On this point $r_{\rm LS}|_{\mu=0}$ where the LS function $\mathcal K$ vanishes,
$I$ must also vanish for satisfying the marginally boundary condition (see Equation [6]),
which in turns indicates a vanishing angular velocity $\Omega$ from
the radiation condition (3), i.e. $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$.
Plugging $\Omega(\mu=0, r= r_{\rm LS}|_{\mu=0}) =0$ back into $\mathcal K = 0$,
we obtain $r_{\rm LS}|_{\mu=0}=2$"

{\bf Finally, a suggestion:
The proof that the inner light cylinder intersects the ergosphere boundary at the equator is
a very nice result (assuming it is correct). A few groups have seen that the current sheet
ends at the ergosphere in full simulations but people seem sheepish about making the claim
because of numerical resolution. The analytical argument is a big help here, so the author
might consider emphasizing the point more somehow.}

To emphasize this point, I have added a sentence in the Summary:

``Especially we find the LS
intersects with the ergosphere at the equator, which was also observed in previous simulations
[e.g. Carrasco2017, East2018] and now we understand its underlying physics. "
